Cartograms with Dynamic Features

### 2022-07-16 paper/section/data.tex
draft: autoref algorithm

After acquiring the shapefiles, we used QGIS \cite{qgisWelcome} to manually adjust projections, translations and scales, and merge them into one shapefile. Finally, mapshaper \cite{blochMapshaper} is used to convert the merged shapefile into a TopoJSON \cite{TopoJSON} file. TopoJSON eliminates redundant coordinates in the data, improving the rendering speed of our implementation.

>>>>

After acquiring the shapefiles, we used QGIS \cite{qgisWelcome} to manually adjust projections, and convert them into GeoJSON files. Finally, mapshaper \cite{blochMapshaper} is used to merge adn convert the GeoJSON files into a TopoJSON \cite{TopoJSON} file. TopoJSON eliminates redundant coordinates in the data, improving the rendering speed of our implementation. See \autoref{table:pre-processing_result} for the pre-processing result.

We describe the above steps in detail in \autoref{app:pre-processing}.
